\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{a4wide}

\title{Application of Graph Neural Networks to Mitigate Popularity Bias in Content Recommendations}
%\author{not specified, not necessary here}
\date{}
\begin{document}
\maketitle

\section*{Literature Review}

\textbf{BiGNN: A Bilateral-Branch Graph Neural Network to Solve Popularity Bias in Recommendation} by Kou et al. introduces a two-branch GNN framework
that effectively distinguishes between popular and long-tail items, improving recommendation fairness, especially in datasets
with imbalanced popularity distributions.

\textbf{MixGCF: An Improved Training Method for Graph Neural Network-based Recommender Systems} by Huang et al. focuses on enhancing the GNN training
process by incorporating user-item interaction information, offering an effective solution for reducing popularity bias but at the cost of increased
computational complexity.

\textbf{XSimGCL: Towards Extremely Simple Graph Contrastive Learning for Recommendation} by Yu et al. simplifies graph contrastive learning methods,
making them more computationally efficient, although it may struggle with capturing complex user-item relationships in large-scale datasets.

\textbf{SimGCL: Graph Contrastive Learning by Finding Homophily in Heterophily} by Liu et al. presents a method for handling both homophilic and
heterophilic relationships in graphs, making it suitable for datasets with diverse types of user-item interactions.

\textbf{An Explicitly Weighted GCN Aggregator based on Temporal and Popularity Features for Recommendation} by Li et al. proposes an explicit
weighting mechanism in GCNs to account for both temporal and popularity-based features, which helps reduce bias in dynamic recommendation environments.

\textbf{Addressing Popularity Bias in Recommender Systems: An Exploration of Self-Supervised Learning Models} by Klimashevskaia et al. explores
self-supervised learning approaches for mitigating popularity bias, offering a promising direction for improving exploration in recommendations
without explicit supervision.

\textbf{A Survey on Popularity Bias in Recommender Systems} by Klimashevskaia et al. provides an extensive survey of methods addressing
popularity bias, summarizing existing solutions and highlighting challenges for future research in this area.

\textbf{Graph Neural Networks in Recommender Systems: A Survey} by Wu et al. offers a comprehensive survey of GNN applications in recommender systems,
providing valuable insights into the theoretical foundations and practical applications of GNNs for addressing bias in recommendations.

\end{document}